Positional surprisal (1-3grams) in CHILDES corpora

### 2019-06-04 surprisal/childes_surprisal.Rmd
slope estimates

  surprisals <- utts %>%
    left_join(unigrams) %>%
    group_by(length, word_order) %>%
    summarise(s = mean(s)) %>%
    ungroup()
}

@@

@@

surprises %>%  
  filter(length == 7, Language == "Japanese") %>%
  ggplot(aes(x = word_order, y = s,
                        color = speaker_role,
                        label = speaker_role)) +
    # facet_grid(Language ~ length, scales = "free") + 
    xlab("Word position") +
    ylab("Mean surprisal") +
    scale_x_continuous(breaks = 1:7) + 
    geom_line(size = 1) +
    geom_point() + 
    theme_classic(base_size = 10) + 
    scale_color_ptol() +
    theme(legend.position = "nones") + 
    geom_text(data = label_data)
```

@@

child_surprisals <- child_utterances %>%
  left_join(child_unigrams) %>%
  mutate(s = -log(p)) %>%
  group_by(length, word_order) %>%
  summarise(s = mean(s))

@@

adult_surprisals <- adult_utterances %>%
  left_join(adult_unigrams) %>%
  mutate(s = -log(p)) %>%
  group_by(length, word_order) %>%
  summarise(s = mean(s))

>>>>

  surprisals <- utts %>%
    left_join(unigrams) %>%
     group_by(length, word_order) %>%
    summarise(mean = mean(log(s)),
              median = median(log(s)),
              se = sd(s)/sqrt(length(s))) %>%
    ungroup()
}

@@

prov_sups %>%
  filter(speaker_role == "child", length == 6, word_order == 3) %>%
  ggplot(aes(x = log(s))) + 
  geom_histogram()
```

@@

child_surprisals %>%  
  filter(length == 12) %>%
  ggplot(aes(x = word_order, y = median)) +
    # facet_grid(Language ~ length, scales = "free") + 
    xlab("Word position") +
    ylab("Mean surprisal") +
    scale_x_continuous(breaks = 1:7) + 
    geom_line(size = 1) +
    geom_pointrange(aes(ymin = mean - 1.96 * se, ymax = mean + 1.96 * se)) + 
    theme_classic(base_size = 10) + 
    scale_color_ptol() +
    theme(legend.position = "nones") #+ 
   # geom_text(data = label_data)
```

@@

child_surprisals <- child_utterances %>%
  left_join(child_unigrams) %>%
  mutate(s = -log(p)) %>%
  group_by(length, word_order) %>%
  summarise(mean = mean(s),
            median = median(s),
            se = sd(s)/sqrt(n()))

@@

adult_surprisals <- adult_utterances %>%
  left_join(adult_unigrams) %>%
  mutate(s = -log(p)) %>%
  group_by(length, word_order) %>%
  summarise(mean = mean(s),
            se = sd(s)/sqrt(n()))
